\documentclass{article}

% Frequently Asked Questions, Notes, ....
% 01) You can use Czech or English to fill in the template.
% 02) Fill in the metadata section.
%

\usepackage[a-2u]{pdfx}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage[ddmmyyyy]{datetime}
\usepackage{geometry}

\renewcommand{\dateseparator}{.}
\renewcommand{\baselinestretch}{1.5}

\geometry{margin=2cm}

\def\ResearchProject{Research project}
\def\CompanyProject{Company project}
\def\SoftwareProject{Software project}

% METADATA SECTION START
\def\StudentsFullName{Ailish Stormwind, Johny Colaborator}
\def\Obor{Computer Science - Software and Data Engineering}
\def\ProjetTitle{My research project}
% Use "\ResearchProject", "\CompanyProject", \SoftwareProject"
\def\ProjectType{\ResearchProject}
\def\SupervisorFullName{Chuck Norris}
\def\ConsultantsFullName{Somemebody Else}
% METADATA SECTION END

\title{\ProjetTitle}
\author{\StudentFullName}

\begin{document}

\centerline{\Large \textbf{Specification of team software project}}
\centerline{ \textbf{Department of Software Engineering}}
\centerline{ \textbf{Faculty of Mathematics and Physics, Charles University}}
\bigskip
{\noindent\begin{tabular*}{\textwidth}{ >{\raggedleft}m{4cm} l}
 {\bf Solvers:} & \StudentsFullName \\
 {\bf Study program:} & \Obor \\
 & \\
 {\bf Project title:} & \ProjetTitle \\
 {\bf Project type:} & \ProjectType \\  
 & \\
 {\bf Supervisor:} & \SupervisorFullName \\  
 {\bf Consultants:} & \ConsultantsFullName \\
\end{tabular*}}

\section{Introduction}
In this section, introduce the research team that you are going to be part of.
Next, introduce the project in which you want to participate.
Explain the objectives of the projects; you may also elaborate on drawbacks, especially if you plan to address any of them.

In a separate paragraph, introduce your project, i.e. your contribution.
Do not venture into details; we get to them later.

\subsection{Relation to other projects}
In this section, explain how your contribution is connected to other projects.

You can also draft the architecture of the existing projects.
Do not describe the architecture of your solution here.

You should also comment on the expected scope and forms of cooperation with other team members.

\section{Project description}
Describe your project in detail.
Most likely the project is not set in stone, and you may need to change things as the project goes.
If that is the case, just provide us with the plan and comment on possible changes.

\subsection{Functional requirements}
List known functional requirements or use-cases.

\subsection{Non-Functional requirements}
List known non-functional requirements.

\subsection{Mockups}
Here, you can showcase mockups, or storyboards (preferred option), and describe the functionality of the screens you plan to implement.

\subsection{Architecture}
Describe the high-level architecture of your solution.
Use a well-known visual notation to describe architecture.
We recommend the first two levels of C4 model - https://c4model.com/.

\section{Platform and technologies}
List technologies, languages, and libraries that you plan to utilize.
This is not a definitive list; later changes are possible.

\section{Risks}
Comment on any uncertainty about the project.
How do you plan to tackle the uncertainty and what are the alternative solutions?

\section{Milestones / Deliverables}
What will be created, what will be presented to the commission, and how?
Is there going to be a demo?
If the project is closed source, how do you provide access to the source code?

\section{Time Schedule}
Here you can comment on the schedule, and reflection of risks, iterations, overlaps, synchronization points, etc..
Do not forget to plan your deployment and especially reserve enough time to create necessary documentation.

\hskip-0.5cm
\begin{tabular}{ | m{11em} | m{23em} | m{2.5cm} | m{1.3cm} | }
   \hline
 Milestone / Deliverable & Activity & Time schedule & Man-days \\
 \hline
 Prototype & Implementation & Month 1 & 20 \\
           & Testing & Month 2 & 4 \\
 \hline
 First version & Implementation & Month 3 - 4 & 40 \\
               & Deployment & Month 4 & 2 \\
               & Documentation & Month 4 & 6 \\
 \hline
 Evaluation & & Month 4 - 5 & 5 \\
 \hline
\end{tabular}

\section{Form of collaboration}
In this section, you should elaborate on how you plan to collaborate with your supervisor as well as other team members.

\subsection{Consulting plan}
Explain the expected time frame for team meetings, that is, how often and how long.
You can also comment on the expected content of the meeting.

\subsection{Collaboration with other team members}
Describe expected interactions with other team members.

\end{document}
